\documentclass[a4paper, 12pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{hyperref} % This package is used to create hyperlinks

% vars 
\def\phone{+44 7544000000}
\def\email{jobs@rubenlopes.uk}

\def\organisation{HP}
\def\position{Software Engener}

\def\customA{supporting open source software development and the opportunity to contribute to the open source community}
\def\customB{on a project like Launchpad and apply my skills in maintaining and expanding large-scale web applications}


\signature{Ruben Lopes}

\begin{document}

\begin{letter}{}

\opening{Dear Hiring Manager at \organisation,}

I am excited to apply for the \position\ position at \organisation. With a solid foundation in software engineering and hands on experience using technologies closely related to products produced by \organisation.

During my industrial placement at HP as a DevOps Engineer, I helped in the developement and deployment a full stack services using Python (Django), and contributed to UI development with React (Typescript). My role also involved managing cloud technologies, such as Docker, and working with CI/CD pipelines using Jenkins and Git, which has provided me with practical experience in building scalable and reliable backend systems. This aligns with \organisation’s work in maintaining and expanding the infrastructure for open source development projects.

At the University of Reading, I have excelled in programming and software development, achieving a First-Class grade in my second year. Through academic projects, including the development of dynamic Android applications and conducting database security practices, I have honed my problem-solving abilities and strengthened my skills in designing and implementing robust architectures. Additionally, working as an AV Assistant during my studies sharpened my troubleshooting skills and enhanced my soft skills in communication and teamwork.

Furthermore, my summer placement as a Computational Scientist at UKRI -- Science and Technology Facilities Council gave me valuable experience in Python and C programming while automating and enhancing features for the \href{https://www.sasview.org/}{Sasview} project. This role also improved my ability to collaborate with global teams, contributing to open-source development.

I am particularly drawn to \organisation\ due to its focus on \customA. I am excited about the chance to work \customB, while further developing my understanding of infrastructure and operations.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with the goals of the team. Please feel free to contact me at \phone\ or via email at  \href{mailto:jobs@rubenlopes.uk}{jobs@rubenlopes.uk}.

\closing{Warm regards, \\ Ruben Lopes}

\end{letter}

\end{document}
