\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem} % For custom itemize settings
\setlength{\parskip}{0pt} % Remove extra space between paragraphs
\setlength{\parindent}{0pt} % No paragraph indent
\usepackage{titlesec} % Custom section title spacing

% Reduce spacing above and below sections
\titlespacing*{\section}{0pt}{1ex}{1ex}
\titlespacing*{\subsection}{0pt}{1ex}{1ex}

\begin{document}

\noindent
\textbf{Ruben Joseph Lopes} \\
\textbf{Phone:} +00 0000 00000 \\
\textbf{Email:} \href{mailto:jobs@rubenlopes.uk}{jobs@rubenlopes.uk} \\
\textbf{LinkedIn:} \href{https://linkedin.com/in/ru4en}{linkedin.com/in/ru4en} \\
\textbf{GitHub:} \href{https://github.com/ru4en}{github.com/ru4en} \\
\textbf{Portfolio:} \href{http://www.rubenlopes.uk}{www.rubenlopes.uk} \\

\vspace{0.3cm} % Reduced from 0.5cm


\section*{Personal Statement}
I am currently pursuing a Bachelor's degree in Computer Science and have valuable hands-on experience in Software Engineering and IT Operations. With a deep-rooted interest and passion for computers and technology, I aspire to pursue a career as a software developer. I enjoy acquiring new skills and applying interdisciplinary knowledge to my work where I can contribute to innovative projects and grow as a professional.

\vspace{0.5cm}

\section*{Experience}

\textbf{HP Inc. - Wolf Security} \\
\textit{DevOps Engineer (Industrial Placement)} \hfill July 2023 – June 2024 \\
In my role as a DevOps Engineer during my industrial placement at HP, I actively utilized React (Typescript) to make UI, used Python with Django to create REST APIs, contributed to the development of internal tools, and scripted in Bash and PowerShell. I was responsible for setting up services for production within virtual environments and gained hands-on experience with cloud technologies like Docker and virtualization. Additionally, I gained hands-on experience with the software development lifecycle by using tools such as Git and Jenkins for setting up CI/CD pipelines.

\begin{itemize}[left=0pt,labelsep=5pt]
    \item Full stack development using Python (Django), PostgreSQL, MySQL, and building UI components using React.js and TypeScript.
    \item Hands-on experience with Linux (Debian-based), scripting in Python, PowerShell, and Bash.
    \item Developed Jenkins CI/CD pipelines using Groovy, Docker, GitHub, and Git.
\end{itemize}

\vspace{0.3cm}

\textbf{University of Reading - IT} \\
\textit{AV (Audio Visual) Assistant} \hfill November 2022 - June 2023 \\
During my tenure as an AV Assistant at the University of Reading, I troubleshooted issues with Windows and audio-visual equipment. This experience enhanced both my technical skills and soft skills, particularly in effective communication and collaborative problem-solving.

\begin{itemize}[left=0pt,labelsep=5pt]
    \item Troubleshooting Windows systems and audio-visual equipment.
\end{itemize}

\vspace{0.3cm}

\textbf{UKRI - Science and Technology Facilities Council} \\
\textit{Computational Scientist (Summer Placement)} \hfill June 2022 - September 2022 \\
I worked on the Sasview project at STFC, automating and improving parts of the software, which allowed me to gain experience in C and Python. I collaborated with software engineers and scientists globally, improving my teamwork and communication skills. I implemented significant features such as UI tabs, batch calculating, 2D data slicing, and data noise reduction using SVD.

\begin{itemize}[left=0pt,labelsep=5pt]
    \item Real-life experience programming in C and Python.
    \item Use of automated testing and version control (Git).
    \item Enhanced skills in planning, presenting, and documentation.
\end{itemize}

\vspace{0.5cm}

\section*{Education}

\textbf{University of Reading - Bachelor’s in Computer Science} \\
\textit{September 2021 - Current (Expected to Graduate in July 2025)} \\
First Year: Upper Second-Class – 68\% \\
\begin{itemize}[left=0pt,labelsep=5pt]
    \item Programming in C/C++: Enhanced skills in C/C++ and Linux commands and Git.
    \item Mathematics and Computation: Scored 85\%, with significant application during my STFC placement.
\end{itemize}
Additional modules: Applications of Computer Science, Fundamentals of Computer Science, Software Engineering, and Student Enterprise. \\

Second Year: First Class – 72\% \\
\begin{itemize}[left=0pt,labelsep=5pt]
    \item Programming in Java: Designed interfaces and developed a dynamic Android application.
    \item Databases and Information Security: Conducted penetration testing, identified vulnerabilities, and organized security strategies.
\end{itemize}
Additional modules: Algorithms and Operating Systems, Compilers, Computer Architecture and Networking, Programming in Python for Data Science, Software System Design with UML, and Service-Oriented System Architecture. \\

\vspace{0.3cm}

\textbf{New College Swindon} \\
\textit{September 2017 - June 2021} \\
GCSE (Maths, English, Physics, Chemistry and Biology) – Grades 4 - 6 \\
BTEC Level 3 In Computing – Distinction Star, Distinction, Distinction (D*DD) \\
During my BTEC award in Computing, I undertook coursework which helped me enhance my writing, coding, and design abilities. My lecturers emphasized best practices, which improved the quality of my work.

\begin{itemize}[left=0pt,labelsep=5pt]
    \item Using Databases and SQL Queries.
    \item The significance of cyber safety and security.
    \item Understanding of the Software Development Life Cycle.
\end{itemize}

\vspace{0.5cm}

\section*{Key Skills}
\begin{itemize}[left=0pt,labelsep=5pt]
    \item Proficiency in GNU/Linux, Windows Server.
    \item Full stack web development using React.js, HTML, CSS, SQL, and JavaScript.
    \item Programming in Java, C, C++, Go, and Python.
    \item Mathematical aptitude and problem-solving skills.
    \item Knowledge of virtualization (Oracle Virtual Box, QEMU) and containerization (Docker).
    \item Shell scripting in Bash, Python, PowerShell.
    \item Experience with microcontrollers and electronics.
    \item Writing tests using Playwright and PyTest.
\end{itemize}

\vspace{0.5cm}

\textbf{References available on request.}

\end{document}
